R Notebook

### 2022-05-30 code.Rmd
Update code.Rmd

models <- data.frame(lm = performance(houseSplit, linearModel), 
                     forward = performance(houseSplit, forwardModel), 
                     backward = performance(houseSplit, backwardModel), 
                     ridge = performance(houseSplit, ridgeModel), 
                     lasso = performance(houseSplit, lassoModel), 
                     ela = performance(dummySplitWithResponse, elasticNetModel), 
                     pcr = performance(dummySplitWithResponse, PCRModel))
models
```

>>>>

models <- data.frame(lm = performance(houseSplit, linearModel), 
                     forward = performance(houseSplit, forwardModel), 
                     backward = performance(houseSplit, backwardModel), 
                     ridge = performance(houseSplit, ridgeModel), 
                     lasso = performance(houseSplit, lassoModel), 
                     ela = performance(dummySplitWithResponse, elasticNetModel), 
                     pcr = performance(dummySplitWithResponse, PCRModel))
models

#make plots for lasso and pcr, our two final models

lassoPlot <- function(df, testSet, lambda) {
  x = as.matrix(select(filter(dummySplit, id != testSet), -id))
  xTest = as.matrix(select(filter(dummySplit, id == testSet), -id))
  y = filter(df, id != testSet)$soldPrice
  yTest = filter(df, id == testSet)$soldPrice
  model <- glmnet(x, y, alpha = 1, lambda = lambda)
  predictions <- predict(model, newx = xTest)
  evalResults(yTest, predictions, filter(df, id == testSet))
}

PCRPlot <- function(df, testSet, ncomp) {
  housePCR <- pcr(soldPrice ~ ., data = select(filter(df, id != testSet), -id), scale = TRUE, validation = "CV", ncomp = ncomp)
  predictions <- predict(housePCR, select(filter(df, id == testSet), -id), ncomp = ncomp)
  yTest <- filter(df, id == testSet)$soldPrice
  return(c(ncomp, round(mean((predictions - yTest)^2)/mean((yTest - mean(yTest))^2),3), round(sqrt(sum((predictions - yTest)^2)/length(predictions)), 3)))
}

performancePlot <- function(df, modelName, parameter) {
  pf <- data.frame(modelName(df, 0, parameter))
  for (i in 1:9) {
    pf <- cbind(pf, modelName(df, i, parameter))
  }
  pf <- t(pf)
  return(list(parameter, mean(pf[,1]), mean(pf[,2])))
}

lassoPerformance <- data.frame(lambda = numeric(), R2 = numeric(), RMSE = numeric())
for (i in seq(-2, 4, by = 0.2)) {
  lassoPerformance[5*(i+2),] <- performancePlot(houseSplit, lassoPlot, 10^i)
}
as.data.frame(lassoPerformance) %>%
  ggplot(aes(x = log10(lambda), y = R2)) +
  geom_line()
as.data.frame(lassoPerformance) %>%
  ggplot(aes(x = log10(lambda), y = RMSE)) +
  geom_line()

PCRPerformance <- data.frame(ncomp = numeric(), R2 = numeric(), RMSE = numeric())
for (i in seq(1, 61)) {
  PCRPerformance[i,] <- performancePlot(dummySplitWithResponse, PCRPlot, i)
}
as.data.frame(PCRPerformance) %>%
  ggplot(aes(x = ncomp, y = R2)) +
  geom_line()
as.data.frame(PCRPerformance) %>%
  ggplot(aes(x = ncomp, y = RMSE)) +
  geom_line()
```
